\documentclass[12pt,twoside]{report}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\graphicspath{ {images/} }
\usepackage{float}
\usepackage[a4paper,width=160mm,top=25mm,bottom=25mm,bindingoffset=6mm]{geometry}
\usepackage{setspace}
\pagenumbering{roman}
\usepackage{url}
\usepackage{gensymb}
\usepackage{bm}
\usepackage{subcaption}
\usepackage{chngcntr}
\counterwithin{figure}{chapter}
\raggedbottom
\usepackage{natbib}
\usepackage{setspace}


\newcommand{\mychapter}[2]{
    \setcounter{chapter}{#1}
    \setcounter{section}{0}
    \chapter*{#2}
    \addcontentsline{toc}{chapter}{#2}
}

\usepackage{titlesec}
\titleformat{\chapter}[display]   
{\normalfont\huge\bfseries}{\chaptertitlename\ \thechapter}{18pt}{\Huge}   
\titlespacing*{\chapter}{0pt}{-20pt}{20pt}

\title{
{Research Plan}\\
{\large Department of Earth Sciences }\\
{\large University of Edinburgh}\\
{\small Submitted in partial fulfilment of the requirements of Doctorate in Earth Observations at the University of Edinburgh.}\\
}
\author{Morag Gray Fotheringham}
\date{2020}

\begin{document}
\onehalfspacing
\maketitle 

\chapter*{Things to Include}
\begin{itemize}
\item Literature review
\item Chapter by chapter plan?
\item Hypotheses
\item Research Questions
\item Predictions
\item Anticipated results
\item What those results might mean?
\item Conceptual figures
\item References
\item Gantt Chart of your timeline
\end{itemize}
 
\chapter*{How to come up with ideas?}
\begin{itemize}
\item What are the current views that are being expressed?
\item Are there any gaps in existing knowledge on the topic that could be addressed?
\item Has the research you propose been done before?
\item What interesting areas do they appear to have overlooked?
\item Are there alternative lines of enquiry beyond those already indicated which seem not to have been
explored?
\item What are the areas of dispute in the subject?
\item Are there inconclusive or contradictory data?
\item What are the underlying assumptions in which others have viewed the context of their work? Are
these flawed?
\end{itemize}

\tableofcontents

\mychapter{1}{Pitch}
\pagenumbering{arabic}

\section{Main research aim:}
The aim of the research is to identify connections and processes linking loss of land-ice to processes in the ocean, atmosphere and sea ice across the Arctic region.


The Hook: what is know about your general field: the big picture?

The knowledge gap: WHat is not known about your gneral field?

The motivation how are we going to do this?

The take home message: here's why this matters?

\mychapter{2}{Literature Review}
\input{Chapters/Litreview}

\mychapter{3}{Chapter 1}
\pagenumbering{arabic}
\input{Chapters/One}

\mychapter{4}{Chapter 2}
\input{Chapters/Two}
 
\mychapter{5}{Chapter 3}
\input{Chapters/Three}


\bibliographystyle{unsrt}
\bibliography{research}

\end{document}


